localhierarchy

### 2025-11-25 README.Rmd
update readme
fix URLs

-   `localhierarchy` depends on `cmdstanr:` Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

@@

See article.

@@

>>>>

-   `localhierarchy` depends on `cmdstanr`: Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

@@

See [article](https://alkemalab.github.io/localhierarchy/articles/localhierarchy_article.html) on package website, at [https://alkemalab.github.io/localhierarchy](https://alkemalab.github.io/localhierarchy/index.html){.uri}.

@@

## Funding
This work was supported, in whole or in part, by the Bill & Melinda Gates Foundation (INV-00844).
